---
title: "Hugh Cross's CV"
author: Hugh Cross
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
---

<!-- import Monserrat and PT Serif Google fonts -->
<style>
  @import url('https://fonts.googleapis.com/css?family=Montserrat&display=swap');
  @import url('https://fonts.googleapis.com/css?family=PT+Serif&display=swap');
</style>



```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(glue)
library(tidyverse)

# Set this to true to have links turned into footnotes at the end of the document
PDF_EXPORT <- TRUE

# Holds all the links that were inserted for placement at the end
links <- c()

source('parsing_functions.R')

# Load csv with position info
position_data <- read_csv('positions.csv')
```


```{r}
# When in export mode the little dots are unaligned, so fix that. 
if(PDF_EXPORT){
  cat("
  <style>
  :root{
    --decorator-outer-offset-left: -6.5px;
  }
  </style>")
}
```


Aside
================================================================================




```{r}
# When in export mode the little dots are unaligned, so fix that. 
if(PDF_EXPORT){
  cat("View this CV online with links at [_hughcross.github.io/cv_](https://hughcross.github.io/cv.html)")
} else {
  cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://https://github.com/hughcross/cv/Cross_CV.pdf)")
}
```

Contact {#contact}
--------------------------------------------------------------------------------


- <i class="fa fa-envelope"></i> hughbcross@gmail.com
- <i class="fa fa-github"></i> [github.com/hughcross](https://github.com/hughcross)
- <i class="fa fa-link"></i> [hughcross.github.io/](https://hughcross.github.io/)
- <i class="fa fa-phone"></i> +64 (0) 21 980 027





Programming Skills {#skills}
--------------------------------------------------------------------------------

```{r}
skills <- tribble(
  ~skill,               ~level,
  "Python",                  5,
  "Jupyter",                  4.5,
  "Bash",                4,
  "R",             3.5,
  "SQL",               2.5,
  "HTML/CSS",               1.5
)

build_skill_bars(skills)
```




Fieldwork {#fieldwork}
--------------------------------------------------------------------------------

- Australia
- Costa Rica
- Mexico
- USA: Colorado and Hawaii



Foreign Language {#foreign-language}
--------------------------------------------------------------------------------

Fluent in Spanish

<br>


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made with [**pagedown**](https://github.com/rstudio/pagedown) in R.

Source code: [github.com/hughcross/cv](https://github.com/hughcross/cv).

Last updated on `r Sys.Date()`.




Main
================================================================================

Hugh Cross, PhD {#title}
--------------------------------------------------------------------------------
  

```{r text.align="justify"}
intro_text <- "I am a computational biologist with a background in ecology and evolutionary genetics. I work on projects across the tree of life, utilising many kinds of data and multiple approaches. With biodiversity studies as a centerpoint, I have naturally come to specialise in metagenomics research. To study any environment is to study a community of genes engaged in molecular dialogues--both within and between species, and this requires a community of researchers working together. I hope to find this team.

"

cat(sanitize_links(intro_text))
```



Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'education')
```





Support and Awards {data-icon=award data-concise=true}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'awards')
```


<br>






<i class="fas fa-chart-area"></i> Professional & Research Experience {data-icon=NULL}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'professional_research_positions')
```





Publications {data-icon=book}
--------------------------------------------------------------------------------

::: aside
**Publications Overview:**

- Citations: 1400

- h-index: 14

- [Google Scholar profile](https://scholar.google.no/citations?user=yynx4lsAAAAJ&hl=en)
:::



```{r}
print_section(position_data, 'academic_articles')
```




\newpage

Teaching Experience {data-icon=tree}
--------------------------------------------------------------------------------

::: aside
- Certified Software Carpentry Instructor

- [link to environmental DNA workshop](https://otagoedna.github.io/edna_workshop_june2021/)

- I also run a [biweekly bioinformatics help session](https://otagomohio.github.io/hacky2021/)
:::

```{r}
print_section(position_data, 'teaching_leadership_positions')
```


<br>


<i class="fas fa-microphone-alt"></i> Selected Abstracts and Presentations {data-icon=NULL}
--------------------------------------------------------------------------------



```{r}
print_section(position_data, 'presentation_abstracts')
```



<br>


<i class="fas fa-solid fa-users"></i> Symposia and Workshops Organised {data-icon=NULL}
--------------------------------------------------------------------------------



```{r}
print_section(position_data, 'symposia_organised')
```




<br>




